Metascatter: Unifying Symbiotic Radio and Intelligent Reflecting Surface

### 2022-07-16 main.tex
:construction: Update literature review

\usepackage{adjustbox}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{array}
\usepackage{circuitikz}
\usepackage{cite}
\usepackage{colortbl}
\usepackage{environ}
\usepackage{fixmath}
\usepackage{grffile}
\usepackage{hyperref}
\usepackage{import}
\usepackage{mathtools}
\usepackage{microtype}
\usepackage{multirow}
\usepackage{pgffor}
\usepackage{pgfgantt}
\usepackage{pgfplots}
\usepackage{physics}
\usepackage{siunitx}
\usepackage{stfloats}
\usepackage{tcolorbox}
\usepackage{tikz}
\usepackage{url}
\usepackage{xcolor}
\usepackage[T1]{fontenc}
\usepackage[acronym]{glossaries-extra}
\usepackage[caption=false,font=footnotesize,subrefformat=parens,labelformat=parens]{subfig}
\usepackage[short]{optidef}
\usepackage[subtle]{savetrees}

@@

	To the best of our knowledge, most existing \gls{sr} systems \cite{Yang2018,Guo2019b,Ding2020,Long2020a,Zhou2019a,Wu2021a,Xu2021a} assumed Gaussian codebook at backscatter nodes, and considered \gls{sic} from primary to backscatter link.
	% It thus requires non-coherent primary encoding at transmitters, and re-encoding, precoding, and subtraction operations that may not be available to legacy receivers.
	It thus requires non-coherent encoding at the transmitter and re-encoding, precoding, and subtraction processes at the receiver.
	Besides, the advantage of \gls{sic} is questionable because 1) the primary and backscatter symbols are mixed by multiplication instead of superposition, and 2) the backscatter symbol period is typically much longer under physical constraints.
	% Motivated by above, we propose a novel Metascatter network where multiple battery-free tags ride over a conventional point-to-point system and adapt their input probability distribution to simultaneously act as backscatter tags of \gls{sr} and reflecting elements of \gls{irs}.
	Motivated by those, we introduce Metascatter that adapts the input distribution of a finite-state passive backscatter node based on \gls{csi} to unify backscatter sources of \gls{sr} and reflecting elements of \gls{irs}.
	% An application scenario was considered where multiple Metascatters are introduced to conventional point-to-point system and adapt their input probability distribution to simultaneously act as backscatter tags of \gls{sr} and reflecting elements of \gls{irs}.
	% An application scenario was considered where multiple Metascatters ride over a point-to-point transmission and simultaneously perform backscatter encoding and passive beamforming.
	An application scenario was considered where multiple Metascatters ride over a point-to-point transmission to simultaneously encode self message and perform passive beamforming.
	To fully accommodate backscatter characteristics, we also propose a novel receiving strategy that first jointly decodes all Metascatter based on average received power, then models their reflection patterns and backscatter paths within equivalent channel for primary decoding.
	% minor modifications on existing receivers, easy to perform, fits backscatter characteristics.
	The contributions of this paper is summarized as follows.

	\emph{First,} Metascatter adapts the input probability distribution of a finite-state backscatter device based on the primary and backscatter \gls{csi}.
	It generalizes the backscatter tags of \gls{sr} and reflecting elements of \gls{irs} to improve the primary-backscatter tradeoff in a flexible manner.
	When the primary link is absolutely prioritized, the tag input probability boils down to \num{1} at the state that maximizes the equivalent channel strength and \num{0} at other states, which is essentially the phase shift selection of an \gls{irs} element.
	When we only care about the backscatter performance, the network boils down to a multi-tag \gls{ambc} and the input design can be simplified accordingly.

>>>>

\usepackage{adjustbox}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{array}
\usepackage{bookmark}
\usepackage{circuitikz}
\usepackage{cite}
\usepackage{colortbl}
\usepackage{environ}
\usepackage{fixmath}
\usepackage{grffile}
\usepackage{hyperref}
\usepackage{import}
\usepackage{mathtools}
\usepackage{microtype}
\usepackage{multirow}
\usepackage{pgffor}
\usepackage{pgfgantt}
\usepackage{pgfplots}
\usepackage{physics}
\usepackage{siunitx}
\usepackage{stfloats}
\usepackage{tcolorbox}
\usepackage{tikz}
\usepackage{url}
\usepackage{xcolor}
\usepackage[T1]{fontenc}
\usepackage[acronym]{glossaries-extra}
\usepackage[caption=false,font=footnotesize,subrefformat=parens,labelformat=parens]{subfig}
\usepackage[short]{optidef}
\usepackage[subtle]{savetrees}

@@

	To the best of our knowledge, most existing \gls{sr} systems \cite{Yang2018,Guo2019b,Ding2020,Long2020a,Zhou2019a,Wu2021a,Xu2021a} assumed Gaussian codebook at backscatter nodes and considered \gls{sic} from primary to backscatter link.
	% It thus requires non-coherent primary encoding at transmitters, and re-encoding, precoding, and subtraction operations that may not be available to legacy receivers.
	It thus requires non-coherent encoding at the transmitter and re-encoding, precoding, and subtraction at the receiver.
	Besides, the advantage of \gls{sic} is questionable because 1) the primary and backscatter symbols are mixed by multiplication instead of superposition, and 2) the backscatter symbol period is typically much longer under physical constraints.
	% Motivated by above, we propose a novel Metascatter network where multiple battery-free tags ride over a conventional point-to-point system and adapt their input probability distribution to simultaneously act as backscatter tags of \gls{sr} and reflecting elements of \gls{irs}.
	Motivated by those, we introduce Metascatter that adapts the input distribution of a passive backscatter node to generalize backscatter sources of \gls{sr} and reflecting elements of \gls{irs}.
	% An application scenario was considered where multiple Metascatters are introduced to conventional point-to-point system and adapt their input probability distribution to simultaneously act as backscatter tags of \gls{sr} and reflecting elements of \gls{irs}.
	% An application scenario was considered where multiple Metascatters ride over a point-to-point transmission and simultaneously perform backscatter encoding and passive beamforming.
	An application scenario was considered where multiple Metascatters ride over a point-to-point transmission to simultaneously encode self message and perform passive beamforming.
	To fully accommodate backscatter characteristics, we also propose a novel receiving strategy that first jointly decodes all Metascatter based on average received power, then models their reflection patterns and backscatter paths within equivalent channel for primary decoding.
	% minor modifications on existing receivers, easy to perform, fits backscatter characteristics.
	The contributions of this paper is summarized as follows.

	\emph{First,} Metascatter adapts the input probability distribution of a finite-state passive backscatter device based on primary and (cascaded) backscatter \gls{csi} to unify and generalize parasitic source of \gls{sr} and reflecting elements of \gls{irs}.
	The reflection pattern over time is no longer fully random or deterministic, but smartly distributed to simultaneously encode backscatter message and assist primary transmission.
	% Instead of treating reflection as fully informative/random or fully auxiliary/deterministic,
	One can adjust node input distribution for flexible primary-backscatter tradeoff.
	When the primary link is absolutely prioritized, the tag input probability boils down to \num{1} at the state that maximizes the equivalent channel strength and \num{0} at other states, which is essentially the phase shift selection of an \gls{irs} element.
	When we only care about the backscatter performance, the network boils down to a multi-tag \gls{ambc} and the input design can be simplified accordingly.
